---
title: "Plots_Github"
author: "J. Guibert"
date: "19/11/2022"
output:
  pdf_document:
    number_sections: yes
    toc: yes
---
# Library

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F)
library(tidyverse)
library(ggplot2)
library(Hmisc)
library(corrplot)
library(gridExtra)
library("PerformanceAnalytics")
library(stats)
library(plyr)
library("ggpubr")
library("grid")
```

# Required data sets

```{r, include=FALSE}
WD <- ".."
PATH_OUTPUT <- file.path(WD, "Outputs")
PATH_FUNC <- file.path(WD, "Functions")
PATH_DATA <- file.path(WD, "Data")
PATH_FIG <- file.path(WD, "Figures_and_stats/Figures")
source(file.path(PATH_FUNC, "Prep_obs.R"))

raw_obs <- read.csv(file.path(PATH_DATA, "all_operations_on_fobs_observe_fr_indian.csv"))
Ob7 <- prep.obs(Ob7 = raw_obs)

Ob7 <- Ob7[Ob7$year>2013,]
Ob7 <- Ob7[Ob7$year<2020,]
Ob7_NLOG = Ob7 %>% filter(obj_conv=="NLOG")
Ob7_NLOG$Zone <- as.factor(ifelse(Ob7_NLOG$latitude<(-10),"Moz","Above_10S"))
world <- map_data("world")

NLOG_VE <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE.csv"), header = TRUE)
VE <- NLOG_VE[,c(8,10,12,14,16)]
colnames(VE) <- c("Chla","SST","SLA","FSLE","SSCI")

NLOG_VE_sup_zero <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_sup_zero.csv"), head = T)
NLOG_VE_sup_zero$logNLOG <- log(NLOG_VE_sup_zero$NLOG_stand)

NLOG_VE_sup_zero_Moz <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_sup_zero_Moz.csv"), head = T)
NLOG_VE_sup_zero_North <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_sup_zero_North.csv"), head = T)

NLOG_VE_zero_Moz <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_zero_Moz.csv"), head = T)
NLOG_VE_zero_North <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_zero_North.csv"), head = T)

NLOG_VE_sup_zero_North$chlacr <- scale(NLOG_VE_sup_zero_North$chlamean)
NLOG_VE_sup_zero_North$slacr <- scale(NLOG_VE_sup_zero_North$slamean)
NLOG_VE_sup_zero_North$SSCIcr <- scale(NLOG_VE_sup_zero_North$SSCImean)
NLOG_VE_sup_zero_North$FSLEcr <- scale(NLOG_VE_sup_zero_North$FSLEmean)
NLOG_VE_sup_zero_North$MNcr <- scale(NLOG_VE_sup_zero_North$MNmean)
NLOG_VE_sup_zero_North$logNLOG <- log(NLOG_VE_sup_zero_North$NLOG_stand)

NLOG_VE_sup_zero_Moz$chlacr <- scale(NLOG_VE_sup_zero_Moz$chlamean)
NLOG_VE_sup_zero_Moz$slacr <- scale(NLOG_VE_sup_zero_Moz$slamean)
NLOG_VE_sup_zero_Moz$SSCIcr <- scale(NLOG_VE_sup_zero_Moz$SSCImean)
NLOG_VE_sup_zero_Moz$FSLEcr <- scale(NLOG_VE_sup_zero_Moz$FSLEmean)
NLOG_VE_sup_zero_Moz$MNcr <- scale(NLOG_VE_sup_zero_Moz$MNmean)
NLOG_VE_sup_zero_Moz$logNLOG <- log(NLOG_VE_sup_zero_Moz$NLOG_stand)

LM4_North_chla <- lm(logNLOG ~ chlacr + slacr, data = NLOG_VE_sup_zero_North)
LM5_Moz_chla <- lm(logNLOG ~ slacr, data = NLOG_VE_sup_zero_Moz)

dfMN_epi<-read.csv(file.path(PATH_OUTPUT, "MN_epi_mean.csv"), header = T)
dfMN_u<-read.csv(file.path(PATH_OUTPUT, "MN_umeso_mean.csv"), header = T)
dfMN_mu<-read.csv(file.path(PATH_OUTPUT, "MN_mumeso_mean.csv"), header = T)
dfMN_ml<-read.csv(file.path(PATH_OUTPUT, "MN_mlmeso_mean.csv"), header = T)
dfMN_hml<-read.csv(file.path(PATH_OUTPUT, "MN_hmlmeso_mean.csv"), header = T)

df_eff <- read.csv(file.path(PATH_OUTPUT, "df_eff.csv"), head = T)
df_eff_new <- read.csv(file.path(PATH_OUTPUT, "df_eff_new_100.csv"), head = T)

```

If problems running the plots, think about "dev.off()"

#### IN TEXT FIGURES ####

# Figure 1 : Study area (map)

```{r, echo = T, fig.show='hide'}
fig1 <- ggplot(aes(x=c(35, 85), y=c(-25, 25)), data=Ob7_NLOG) + 
  geom_point(data = Ob7_NLOG, mapping = aes(x = longitude, y = latitude),  
             colour = "blue", shape=1,size=1) + 
  geom_map(data = world, map = world, aes(long, lat, map_id = region),  
           color =  "black", fill = "lightgray", size = 0.1) +
  geom_segment(aes(x=40,y=(-10),xend=85,yend=(-10)),linetype=2)+
  xlim(min(35),max(85))+
  ylim(min(-25),max(25))+
  xlab("Longitude (deg)") +
  ylab("Latitude (deg)")+
  theme(panel.border = element_rect(fill = NA, colour = "black"))+
  theme(text = element_text(size = 15))+
  theme(axis.text.x = element_text(size = 15))+
  theme(axis.text.y = element_text(size = 15))
```

## Save plot

```{r}
ggsave(file=file.path(PATH_FIG, "Fig1_Study Area.png"), fig1,width = 10, height = 10, units = "cm")
ggsave(file=file.path(PATH_FIG, "Fig1.eps"), fig1,width = 10, height = 10, units = "cm")
```

# Figure 2 : Yearly number of NLOG observations (histograms)

```{r}
fig2 <- ggplot(data = Ob7_NLOG) + 
  geom_bar(mapping = aes(x = year, fill=as.factor(Zone)), binwidth=0.5, color = "black", position = position_dodge2(width = 1, preserve = "single", padding = 0))+ 
  stat_count(aes(x = year, y=..count.., fill=as.factor(Zone), label=..count..),size = 6, geom="text", vjust=-0.5, position = position_dodge2(width = 0.9, preserve = "single", padding = 0))+
  ylab("Number of observations")+
  scale_x_continuous(name="Years", breaks=c(2014,2015,2016,2017,2018,2019),  
                     labels = c("2014","2015","2016","2017","2018","2019"))+
  scale_fill_manual(values = c("grey48","grey86"), name = "Zone",  
                    labels = c (">10°S","<10°S"))+
  theme(panel.border = element_rect(fill = NA, colour = "black"))+
  theme(text = element_text(size = 25))+
  theme(axis.text.x = element_text(size = 25))+
  theme(axis.text.y = element_text(size = 25))+
  theme(legend.text = element_text(size=25))+
  theme(legend.key.size = unit(1, 'cm'))
``` 

## Save plot

```{r}
ggsave(file=file.path(PATH_FIG, "Fig2_Nb of NLOGs.png"), fig2,width = 30, height = 18, units = "cm")
ggsave(file=file.path(PATH_FIG, "Fig2.eps"), fig2,width = 30, height = 18, units = "cm")
```

# Figure 3 : Distribution of the environmental variables according to NLOG = 0 or NLOG > 0

## SSCI - Moz

```{r}
## SSCI
#Moz
f3.ssci.moz <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=SSCImean, y = ..density.., fill = "NLOG = 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_zero_Moz, alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=SSCImean, y = ..density.., fill = "NLOG > 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_sup_zero_Moz, alpha = 0.5)+
  scale_fill_manual(name = "NLOG abundance index (Number per observation effort)",  
                    values = c("NLOG = 0" = "steelblue3", "NLOG > 0" = "yellow1"))+
  scale_x_continuous(breaks=c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7))+
  scale_y_continuous(labels = function(x) x*100*b.width)+
  xlab("Mean SSCI (m.s-1)")+
  ylab("Frequency (%)")+
  ggtitle("< 10°S")+
  theme(text = element_text(size = 20))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  annotate(geom="text", x=0.445, y=8.75, label="P = 0.099",
              color="black", fontface="bold.italic", size=6)
```

## SSCI - North

```{r}
## SSCI
#North
f3.ssci.north <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=SSCImean, y = ..density.., fill = "NLOG = 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_zero_North, alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=SSCImean, y = ..density.., fill = "NLOG > 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_sup_zero_North, alpha = 0.5)+
  scale_fill_manual(name = "NLOG abundance index (Number per observation effort)",  
                    values = c("NLOG = 0" = "steelblue3", "NLOG > 0" = "yellow1"))+
  scale_x_continuous(breaks=c(0,0.1,0.2,0.3,0.4,0.5,0.6))+
  scale_y_continuous(labels = function(x) x*100*b.width)+
  xlab("Mean SSCI (m.s-1)")+
  ylab(" ")+
  ggtitle("\U2265 10°S")+ #\U2265 is the code for the >= symbol
  theme(text = element_text(size = 20))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  annotate(geom="text", x=0.62, y=4.3, label="P = 0.013",
              color="black", fontface="bold.italic", size=6)
```

## SLA - Moz

```{r}
## SLA
#Moz
f3.sla.moz <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=slamean, y = ..density.., fill = "NLOG = 0"),  
                 binwidth = 0.02,  bins = 30, size = 1,  
                 data = NLOG_VE_zero_Moz, alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=slamean, y = ..density.., fill = "NLOG > 0"),  
                 binwidth = 0.02,  bins = 30, size = 1,  
                 data = NLOG_VE_sup_zero_Moz, alpha = 0.5)+
  scale_fill_manual(name = "NLOG abundance index (Number per observation effort)",  
                    values = c("NLOG = 0" = "steelblue3", "NLOG > 0" = "yellow1"))+
  scale_x_continuous(breaks=c(-0.10,-0.05,0,0.05,0.10,0.15,0.20,0.25,0.30))+
  scale_y_continuous(labels = function(x) x*100*b.width)+
  xlab("Mean SLA (m)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  annotate(geom="text", x=0.14, y=13, label="P = 0.345",
              color="black", fontface="bold.italic", size=6)
```

## SLA - North

```{r}
## SLA
#North
f3.sla.north <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=slamean, y = ..density.., fill = "NLOG = 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_zero_North, alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=slamean, y = ..density.., fill = "NLOG > 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_sup_zero_North, alpha = 0.5)+
  scale_fill_manual(name = "NLOG abundance index (Number per observation effort)",  
                    values = c("NLOG = 0" = "steelblue3", "NLOG > 0" = "yellow1"))+
  scale_x_continuous(breaks=c(-0.10,-0.05,0,0.05,0.10,0.15,0.20,0.25,0.30))+
  scale_y_continuous(labels = function(x) x*100*b.width)+
  xlab("Mean SLA (m)")+
  ylab(" ")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 18))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  annotate(geom="text", x=0.28, y=5, label="P = 0.292",
              color="black", fontface="bold.italic", size=6)
```

## FSLE - Moz

```{r}
## FSLE
#Moz
f3.fsle.moz <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=FSLEmean, y = ..density.., fill = "NLOG = 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_zero_Moz, alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=FSLEmean, y = ..density.., fill = "NLOG > 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_sup_zero_Moz, alpha = 0.5)+
  scale_fill_manual(name = "NLOG abundance index (Number per observation effort)",  
                    values = c("NLOG = 0" = "steelblue3", "NLOG > 0" = "yellow1"))+
  scale_x_continuous(breaks=c(-0.14,-0.12,-0.10,-0.08,-0.06,-0.04,-0.02,0))+
  scale_y_continuous(labels = function(x) x*100*b.width)+
  xlab("Mean FSLE (days-1)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  annotate(geom="text", x=-0.037, y=15, label="P = 0.114",
              color="black", fontface="bold.italic", size=6)
```

## FSLE - North

```{r}
## FSLE
#North
f3.fsle.north <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=FSLEmean, y = ..density.., fill = "NLOG = 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_zero_North, alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=FSLEmean, y = ..density.., fill = "NLOG > 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_sup_zero_North, alpha = 0.5)+
  scale_fill_manual(name = "NLOG abundance index (Number per observation effort)",  
                    values = c("NLOG = 0" = "steelblue3", "NLOG > 0" = "yellow1"))+
  scale_x_continuous(breaks=c(-0.14,-0.12,-0.10,-0.08,-0.06,-0.04,-0.02,0))+
  scale_y_continuous(labels = function(x) x*100*b.width)+
  xlab("Mean FSLE (days-1)")+
  ylab(" ")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  annotate(geom="text", x=0, y=21, label="P = 0.291",
              color="black", fontface="bold.italic", size=6)
```

## MN_Epi - Moz

```{r}
## MN_Epi
#Moz
f3.mn.moz <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=MNmean, y = ..density.., fill = "NLOG = 0"),  
                 binwidth = 0.04,  bins = 30, size = 1,  
                 data = NLOG_VE_zero_Moz, alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=MNmean, y = ..density.., fill = "NLOG > 0"),  
                 binwidth = 0.04,  bins = 30, size = 1,  
                 data = NLOG_VE_sup_zero_Moz, alpha = 0.5)+
  scale_fill_manual(name = "NLOG abundance index (Number per observation effort)",  
                    values = c("NLOG = 0" = "steelblue3", "NLOG > 0" = "yellow1"))+
  scale_x_continuous(breaks=c(0.25,0.50,0.75,1.00,1.25))+
  scale_y_continuous(labels = function(x) x*100*b.width)+
  xlab("Mean MN_Epi (g.m-2)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  annotate(geom="text", x=1.2, y=4.5, label="P = 0.669",
              color="black", fontface="bold.italic", size=6)
```

## MN_Epi - North

```{r}
## MN_Epi
#North
f3.mn.north <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=MNmean, y = ..density.., fill = "NLOG = 0"),  
                 binwidth = 0.025, size = 1,  
                 data = NLOG_VE_zero_North, alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=MNmean, y = ..density.., fill = "NLOG > 0"),  
                 binwidth = 0.025, size = 1,  
                 data = NLOG_VE_sup_zero_North, alpha = 0.5)+
  scale_fill_manual(name = "NLOG abundance index (Number per observation effort)",  
                    values = c("NLOG = 0" = "steelblue3", "NLOG > 0" = "yellow1"))+
  scale_x_continuous(breaks=c(0.3,0.6,0.9))+
  scale_y_continuous(labels = function(x) x*100*b.width)+
  xlab("Mean MN_Epi (g.m-2)")+
  ylab(" ")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  annotate(geom="text", x=1.04, y=2.8, label="P = 0.160",
              color="black", fontface="bold.italic", size=6)
```

## Chla - Moz

```{r}
## Chla
#Moz
b.width = 0.02
f3.chla.moz <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=chlamean, y = ..density.., fill = "NLOG = 0"),  
                 binwidth = b.width, bins = 30, size = 1,  
                 data = NLOG_VE_zero_Moz, alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=chlamean, y = ..density.., fill = "NLOG > 0"),  
                 binwidth = b.width, bins = 30, size = 1,  
                 data = NLOG_VE_sup_zero_Moz, alpha = 0.5)+
  scale_fill_manual(name = "NLOG abundance index (Number per observation effort)",  
                    values = c("NLOG = 0" = "steelblue3", "NLOG > 0" = "yellow1"))+
  scale_x_continuous(breaks=c(0,0.10,0.20,0.30,0.40,0.50,0.60,0.70,0.80,0.90,1))+
  scale_y_continuous(labels = function(x) x*100*b.width)+
  xlab("Mean Chl-a (mg.m-3)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  annotate(geom="text", x=0.93, y=9.1, label="P = 0.441",
              color="black", fontface="bold.italic", size=6)
```

## Chla - North

```{r}
## Chla
#North
f3.chla.north <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=chlamean, y = ..density.., fill = "NLOG = 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_zero_North, alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=chlamean, y = ..density.., fill = "NLOG > 0"),  
                 binwidth = 0.02, size = 1,  
                 data = NLOG_VE_sup_zero_North, alpha = 0.5)+
  scale_fill_manual(name = "NLOG abundance index (Number per observation effort)",  
                    values = c("NLOG = 0" = "steelblue3", "NLOG > 0" = "yellow1"))+
  scale_x_continuous(breaks=c(0,0.10,0.20,0.30,0.40,0.50,0.60,0.70,0.80,0.90,1))+
  scale_y_continuous(labels = function(x) x*100*b.width)+
  xlab("Mean Chl-a (mg.m-3)")+
  ylab(" ")+
  ggtitle(" ")+ 
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  annotate(geom="text", x=0.69, y=6.5, label="P = 0.012",
              color="black", fontface="bold.italic", size=6)
```

##Combine plots
To combine plots, put each plot in an object (a, b, c, d, e, etc...) and use "grid.arrange(a, b, c, d, e, ncol=2, nrow=3)". You can add labels and use a common legend. It is also possible to use "rremove("ylab")" to avoid the y axis text.

```{r}
fig3 <- ggarrange(f3.ssci.moz, f3.ssci.north,
                     f3.sla.moz, f3.sla.north,
                     f3.fsle.moz,f3.fsle.north, 
                     f3.mn.moz, f3.mn.north,
                     f3.chla.moz, f3.chla.north,
                     labels = c("(a)","(b)","(c)","(d)","(e)","(f)","(g)","(h)","(i)","(j)"),
                     font.label = list(size = 20),
                     label.x = 0.85,
                     label.y = 0.85,
                     ncol = 2, nrow = 5,
                     common.legend = TRUE, legend = "bottom",
                     widths = c(1, 1),
                     heights = c(1, 1))

```

## Save plots
```{r}
ggsave(file=file.path(PATH_FIG, "Fig3_Distributions of VE.png"), fig3,width = 35, height = 50, units = "cm")
ggsave(file=file.path(PATH_FIG, "Fig3.eps"), fig3,width = 35, height = 50, units = "cm")
```

# Figure 4 : Scatter plots : NLOGs vs VE

## SSCI

```{r}
#SSCI
f4.ssci <- ggplot(NLOG_VE_sup_zero)+
  geom_point(aes(x = SSCImean, y = NLOG_stand, shape = Zone),size = 3)+
  scale_shape_manual(values = c(1, 17),label = c(">10°S","<10°S"))+
  scale_x_continuous(breaks=c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7))+
  xlab("Mean SSCI (m.s-1)")+
  ylab("NLOG abundance index 
       (Number per 
       observation effort)")+
  scale_y_continuous(breaks=c(0,0.5,1,1.5,2,2.5))+
  theme(text = element_text(size = 17))+
  theme(axis.text.x = element_text(size = 18))+
  theme(axis.text.y = element_text(size = 18))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(legend.position = "none")+
  theme(legend.key.size = unit(1, 'cm'))      
```

## SLA

```{r}
#SLA
f4.sla <- ggplot(NLOG_VE_sup_zero)+
  geom_point(aes(x = slamean, y = NLOG_stand, shape = Zone),size = 3)+
  scale_shape_manual(values = c(1, 17),label = c(">10°S","<10°S"))+
  scale_x_continuous(breaks=c(-0.10,-0.05,0,0.05,0.10,0.15,0.20,0.25,0.30))+
  xlab("Mean SLA (m)")+
  ylab(" 
        
       ")+
  scale_y_continuous(breaks=c(0,0.5,1,1.5,2,2.5))+
  theme(text = element_text(size = 17))+
  theme(axis.text.x = element_text(size = 16))+
  theme(axis.text.y = element_text(size = 18))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(legend.position = "none")+
  theme(legend.key.size = unit(1, 'cm'))         
```

## FSLE

```{r}
#FSLE
f4.fsle <- ggplot(NLOG_VE_sup_zero)+
  geom_point(aes(x = FSLEmean, y = NLOG_stand, shape = Zone),size = 3)+
  scale_shape_manual(values = c(1, 17),label = c(">10°S","<10°S"))+
  scale_x_continuous(breaks=c(-0.14,-0.12,-0.10,-0.08,-0.06,-0.04,-0.02,0))+
  xlab("Mean FSLE (days-1)")+
  ylab(" 
        
       ")+
  scale_y_continuous(breaks=c(0,0.5,1,1.5,2,2.5))+
  theme(text = element_text(size = 17))+
  theme(axis.text.x = element_text(size = 18))+
  theme(axis.text.y = element_text(size = 18))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(legend.position = "none")+
  theme(legend.key.size = unit(1, 'cm'))        
```

## MN_Epi

```{r}
#MN_Epi
f4.mn <- ggplot(NLOG_VE_sup_zero)+
  geom_point(aes(x = MNmean, y = NLOG_stand, shape = Zone),size = 3)+
  scale_shape_manual(values = c(1, 17),label = c(">10°S","<10°S"))+
  scale_x_continuous(breaks=c(0.25,0.50,0.75,1,1.25))+
  xlab("Mean MN_Epi (g.m-2)")+
  ylab("NLOG abundance index 
       (Number per 
       observation effort)")+
  scale_y_continuous(breaks=c(0,0.5,1,1.5,2,2.5))+
  theme(text = element_text(size = 17))+
  theme(axis.text.x = element_text(size = 18))+
  theme(axis.text.y = element_text(size = 18))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(legend.position = "none")+
  theme(legend.key.size = unit(1, 'cm'))      
```

## Chla
```{r}
#Chla
f4.chla <- ggplot(NLOG_VE_sup_zero)+
  geom_point(aes(x = chlamean, y = NLOG_stand, shape = Zone),size = 3)+
  scale_shape_manual(values = c(1, 17),label = c(">10°S","<10°S"))+
  scale_x_continuous(breaks=c(0,0.10,0.20,0.30,0.40,0.50,0.60,0.70,0.80,0.90,1))+
  xlab("Mean Chl-a (mg.m-3)")+
  ylab("NLOG abundance index 
       (Number per 
       observation effort)")+
  scale_y_continuous(breaks=c(0,0.5,1,1.5,2,2.5))+
  theme(text = element_text(size = 17))+
  theme(axis.text.x = element_text(size = 18))+
  theme(axis.text.y = element_text(size = 18))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(legend.position = "none")+
  theme(legend.key.size = unit(1, 'cm'))
```

##Combine plots

```{r}
fig4 <- ggarrange(f4.ssci,
                     f4.sla, 
                     f4.fsle, 
                     f4.mn,
                     f4.chla,
          labels = c("(a)","(b)","(c)","(d)","(e)"),
                     font.label = list(size = 20),
                     label.x = 0.85,
                     label.y = 0.95,
          ncol = 2, nrow = 3, 
          common.legend = TRUE, legend = "bottom") 

```

## Save plots

```{r}
ggsave(file=file.path(PATH_FIG, "Fig4_Scatter plots.png"), fig4, width = 30, height = 25, units = "cm")
ggsave(file=file.path(PATH_FIG, "Fig4.eps"), fig4, width = 30, height = 25, units = "cm")

```

# Figure 5 : Diagnostic plots of models

```{r}
plot(LM4_North_chla)
plot(LM4_North_chla, which=c(1,2))

plot(LM5_Moz_chla)
plot(LM5_Moz_chla, which=c(1,2))
```


#### APPENDICES FIGURES ####

# Appendix A1 : Distribution of the NLOG abundance index 
## Before log transformation

```{r}
#Before
f.bef <- ggplot()+
  geom_histogram(data = NLOG_VE_sup_zero, aes(x = NLOG_stand), binwidth = 0.1)+
  scale_x_continuous(breaks=c(0,0.5,1,1.5,2,2.5,3))+
  scale_y_continuous(breaks=c(0,25,50,75,100,125,150))+
  xlab("NLOG abundance index
  (Number per observation effort)")+
  ylab("Frequency (%)")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))
```

## After log transformation

```{r}
#After
f.aft <- ggplot()+
  geom_histogram(data = NLOG_VE_sup_zero, aes(x = logNLOG), binwidth = 0.25)+
  scale_x_continuous(breaks=c(-4,-3,-2,-1,0,1,2))+
  scale_y_continuous(breaks=c(0,5,10,15,20,25,30,35,40,45,50))+
  xlab("NLOG abundance index
  (Number per observation effort)")+
  ylab("Frequency (%)")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))
```

##Combine plots

```{r}
ApxA1 <- ggarrange(f.bef, f.aft+
                     rremove("ylab"),
          labels = c("(a)", "(b)"),
          font.label = list(size = 20),
                     label.x = 0.85,
                     label.y = 0.95,
          ncol = 2, nrow = 1) 
```

## Save plots

```{r}
ggsave(file=file.path(PATH_FIG, "Appendix_A1_Aim distribution.png"), ApxA1,width = 30, height = 15, units = "cm")
ggsave(file=file.path(PATH_FIG, "Appendix_A1_Aim distribution.eps"), ApxA1,width = 30, height = 15, units = "cm")

```

# Appendix A2 : correlation matrix of micronekton types

```{r}
my_list <- list(dfMN_epi,dfMN_u,dfMN_mu,dfMN_ml,dfMN_hml)
df <- Reduce(function(x, y) merge(x, y, by=c("lat_grid", "lon_grid", "year", "month")), my_list)  
names(df)
my_data_mn <- df %>% dplyr::select(micronec_epi, micronec_umeso, micronec_mumeso, micronec_mlmeso, micronec_hmlmeso)
colnames(my_data_mn) <- c("MN_Epi","MN_Um","MN_Mum","MN_Mlm","MN_Hmlm")
chart.Correlation(my_data_mn, histogram=TRUE, pch=20, method = "kendall")
```

# Appendix A3 : correlation matrix of Environmental variables (VE)

```{r}
names(NLOG_VE)
my_data_ve <- NLOG_VE %>% dplyr::select(sstmean, SSCImean, slamean, FSLEmean, MNmean, chlamean)
colnames(my_data_ve) <- c("SST","SSCI","SLA","FSLE", "MN_Epi","Chl-a")
chart.Correlation(my_data_ve, histogram=TRUE, pch=20, method = "kendall")
```

# Appendix A4 : Predicted vs Observed Aim values
## North

```{r}
#North
pred.north <- predict(LM4_North_chla)
NLOG_VE_sup_zero_North$pred<-pred.north
A4.north <- ggplot(NLOG_VE_sup_zero_North, aes(x = logNLOG, y = pred))+
  geom_point()+
  xlim(min(NLOG_VE_sup_zero_North$logNLOG),max(NLOG_VE_sup_zero_North$logNLOG))+
  ylim(min(NLOG_VE_sup_zero_North$logNLOG),max(NLOG_VE_sup_zero_North$logNLOG))+
  geom_abline(slope = 1, intercept = 0)+
  xlab("Observed NLOG abundance index")+
  ylab("Predicted NLOG abundance index")+
  theme(text = element_text(size = 15))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))
```

## Moz

```{r}
#Moz
pred.moz <- predict(LM5_Moz_chla)
NLOG_VE_sup_zero_Moz$pred<-pred.moz
A4.moz <- ggplot(NLOG_VE_sup_zero_Moz, aes(x = logNLOG, y = pred))+
  geom_point()+
  xlim(min(NLOG_VE_sup_zero_Moz$logNLOG),max(NLOG_VE_sup_zero_Moz$logNLOG))+
  ylim(min(NLOG_VE_sup_zero_Moz$logNLOG),max(NLOG_VE_sup_zero_Moz$logNLOG))+
  geom_abline(slope = 1, intercept = 0)+
  xlab("Observed NLOG abundance index")+
  ylab("Predicted NLOG abundance index")+
  theme(text = element_text(size = 15))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))

```

##Combine plots

```{r}
ApxA4 <- ggarrange(A4.north, A4.moz+
                     rremove("ylab"),
          labels = c("(a)", "(b)"),
          font.label = list(size = 20),
                     label.x = 0.1,
                     label.y = 0.95,
          ncol = 2, nrow = 1) 
```

## Save plots

```{r}
ggsave(file=file.path(PATH_FIG, "Appendix_A4_pred vs obs.png"), ApxA4, width = 35, height = 10, units = "cm")
ggsave(file=file.path(PATH_FIG, "Appendix_A4_pred vs obs.eps"), ApxA4,width = 35, height = 10, units = "cm")
```

# Appendix B1 : Distribution of the environmental variables according to used data or rendom data

## SSCI - Moz

```{r}
## SSCI
#Moz
B1.ssci.moz <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=SSCImean, y = ..density.., fill = "Data used"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="Moz",], alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=SSCImean, y = ..density.., fill = "Random data"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff_new[df_eff_new$Zone=="Moz",], alpha=0.5)+
  scale_fill_manual(name = "Data used vs Random data",
                    values = c("Random data" = "yellow1", "Data used" = "steelblue"))+
  xlab("Mean SSCI (m.s-1)")+
  ylab("Frequency (%)")+
  ggtitle("< 10°S")+
    theme(text = element_text(size = 20))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(plot.margin = grid::unit(c(0,0.75,0,0), "cm"))
```

## SSCI - North

```{r}
## SSCI
#North
B1.ssci.north <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=SSCImean, y = ..density.., fill = "Data used"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="Above_10S",], alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=SSCImean, y = ..density.., fill = "Random data"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff_new[df_eff_new$Zone=="Above_10S",], alpha=0.5)+
  scale_fill_manual(name = "Data used vs Random data",
                    values = c("Random data" = "yellow1", "Data used" = "steelblue"))+
  xlab("Mean SSCI (m.s-1)")+
  ylab("Frequency (%)")+
  ggtitle("\U2265 10°S")+ #\U2265 is the code for the >= symbol
  theme(text = element_text(size = 20))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(plot.margin = grid::unit(c(0,0.75,0,0), "cm"))
```

## SLA - Moz

```{r}
## SLA
#Moz
B1.sla.moz <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=slamean, y = ..density.., fill = "Data used"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="Moz",], alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=slamean, y = ..density.., fill = "Random data"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff_new[df_eff_new$Zone=="Moz",], alpha=0.5)+
  scale_fill_manual(name = "Data used vs Random data",
                    values = c("Random data" = "yellow1", "Data used" = "steelblue"))+
  xlab("Mean SLA (m)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(plot.margin = grid::unit(c(0,0.75,0,0), "cm"))
```

## SLA - North

```{r}
## SLA
#North
B1.sla.north <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=slamean, y = ..density.., fill = "Data used"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="Above_10S",], alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=slamean, y = ..density.., fill = "Random data"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff_new[df_eff_new$Zone=="Above_10S",], alpha=0.5)+
  scale_fill_manual(name = "Data used vs Random data",
                    values = c("Random data" = "yellow1", "Data used" = "steelblue"))+
  xlab("Mean SLA (m)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(plot.margin = grid::unit(c(0,0.75,0,0), "cm"))
```

## FSLE - Moz

```{r}
## FSLE
#Moz
B1.fsle.moz <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=FSLEmean, y = ..density.., fill = "Data used"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="Moz",], alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=FSLEmean, y = ..density.., fill = "Random data"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff_new[df_eff_new$Zone=="Moz",], alpha=0.5)+
  scale_fill_manual(name = "Data used vs Random data",
                    values = c("Random data" = "yellow1", "Data used" = "steelblue"))+
  xlab("Mean FSLE (days-1)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(plot.margin = grid::unit(c(0,0.75,0,0), "cm"))
```

## FSLE - North

```{r}
## FSLE
#North
B1.fsle.north <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=FSLEmean, y = ..density.., fill = "Data used"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="Above_10S",], alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=FSLEmean, y = ..density.., fill = "Random data"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff_new[df_eff_new$Zone=="Above_10S",], alpha=0.5)+
  scale_fill_manual(name = "Data used vs Random data",
                    values = c("Random data" = "yellow1", "Data used" = "steelblue"))+
  xlab("Mean FSLE (days-1)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(plot.margin = grid::unit(c(0,0.75,0,0), "cm"))
```

## MN_Epi - Moz

```{r}
## MN_Epi
#Moz
B1.mn.moz <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=micronec_epi, y = ..density.., fill = "Data used"),
                 binwidth = 0.04, bins = 30, size = 1,
                 data = df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="Moz",], alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=micronec_epi, y = ..density.., fill = "Random data"),
                 binwidth = 0.04, bins = 30, size = 1,
                 data = df_eff_new[df_eff_new$Zone=="Moz",], alpha=0.5)+
  scale_fill_manual(name = "Data used vs Random data",
                    values = c("Random data" = "yellow1", "Data used" = "steelblue"))+
  xlab("Mean MN_Epi (g.m-2)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(plot.margin = grid::unit(c(0,0.75,0,0), "cm"))
```

## MN_Epi - North 

```{r}
## MN_Epi
#North
B1.mn.north <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=micronec_epi, y = ..density.., fill = "Data used"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="Above_10S",], alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=micronec_epi, y = ..density.., fill = "Random data"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff_new[df_eff_new$Zone=="Above_10S",], alpha=0.5)+
  scale_fill_manual(name = "Data used vs Random data",
                    values = c("Random data" = "yellow1", "Data used" = "steelblue"))+
  xlab("Mean MN_Epi (g.m-2)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(plot.margin = grid::unit(c(0,0.75,0,0), "cm"))

```

## Chla - Moz

```{r}
## Chla
#Moz
B1.chla.moz <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=chlamean, y = ..density.., fill = "Data used"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="Moz",], alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=chlamean, y = ..density.., fill = "Random data"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff_new[df_eff_new$Zone=="Moz",], alpha=0.5)+
  scale_fill_manual(name = "Data used vs Random data",
                    values = c("Random data" = "yellow1", "Data used" = "steelblue"))+
  xlab("Mean Chl-a (mg.m-3)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(plot.margin = grid::unit(c(0,0.75,0,0), "cm"))

```

## Chla - North

```{r}
## Chla
#North
B1.chla.north <- ggplot()+
  geom_histogram(stat = 'bin', aes(x=chlamean, y = ..density.., fill = "Data used"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="Above_10S",], alpha=0.5)+
  geom_histogram(stat = 'bin', aes(x=chlamean, y = ..density.., fill = "Random data"),
                 binwidth = 0.02, bins = 30, size = 1,
                 data = df_eff_new[df_eff_new$Zone=="Above_10S",], alpha=0.5)+
  scale_fill_manual(name = "Data used vs Random data",
                    values = c("Random data" = "yellow1", "Data used" = "steelblue"))+
  xlab("Mean Chl-a (mg.m-3)")+
  ylab("Frequency (%)")+
  ggtitle(" ")+
  theme(text = element_text(size = 20))+
  theme(axis.text.x = element_text(size = 20))+
  theme(axis.text.y = element_text(size = 20))+
  theme(legend.text = element_text(size=20))+
  theme(legend.title = element_text(size=20))+
  theme(plot.margin = grid::unit(c(0,0.75,0,0), "cm"))
```

##Combine plots

```{r}
ApxB1 <- ggarrange(B1.ssci.moz, B1.ssci.north + rremove("ylab"),
                     B1.sla.moz, B1.sla.north + rremove("ylab"),
                     B1.fsle.moz, B1.fsle.north + rremove("ylab"), 
                     B1.mn.moz, B1.mn.north + rremove("ylab"),
                     B1.chla.moz, B1.chla.north + rremove("ylab"),
                     labels = c("(a)","(b)","(c)","(d)","(e)","(f)","(g)","(h)","(i)","(j)"),
                     font.label = list(size = 20),
                     label.x = 0.85,
                     label.y = 0.90,
                     ncol = 2, nrow = 5,
                     common.legend = TRUE, legend = "bottom",
                     widths = c(1, 1),
                     heights = c(1, 1))
```

## Save plots

```{r}
ggsave(file=file.path(PATH_FIG, "Appendix_B1_sampling bias.png"), ApxB1,width = 35, height = 50, units = "cm")
ggsave(file=file.path(PATH_FIG, "Appendix_B1_sampling bias.eps"), ApxB1,width = 35, height = 50, units = "cm")
```

