---
title: "Statistical analyses"
author: "J. Guibert & A. Dupaix"
date: "20/11/2022 - update 23/05/2024"
output: pdf_document
toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F) 
library(MASS)
library(mgcv)
```

\newpage

# Required data sets

```{r data frame}
WD <- ".."
PATH_OUTPUT <- file.path(WD, "Outputs")
PATH_FUNC <- file.path(WD, "Functions")
source(file.path(PATH_FUNC, "stepAIC_gam.R"))

NLOG_VE <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE.csv"), head = T)
NLOG_VE_sup_zero <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_sup_zero.csv"), head = T)
NLOG_VE_sup_zero_Moz <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_sup_zero_Moz.csv"), head = T)
NLOG_VE_sup_zero_North <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_sup_zero_North.csv"), head = T)

NLOG_VE_zero <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_zero.csv"), head = T)

NLOG_VE_zero_Moz <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_zero_Moz.csv"), head = T)
NLOG_VE_zero_North <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_zero_North.csv"), head = T)

dfMN_epi<-read.csv(file.path(PATH_OUTPUT, "MN_epi_mean.csv"), header = T)
dfMN_u<-read.csv(file.path(PATH_OUTPUT, "MN_umeso_mean.csv"), header = T)
dfMN_mu<-read.csv(file.path(PATH_OUTPUT, "MN_mumeso_mean.csv"), header = T)
dfMN_ml<-read.csv(file.path(PATH_OUTPUT, "MN_mlmeso_mean.csv"), header = T)
dfMN_hml<-read.csv(file.path(PATH_OUTPUT, "MN_hmlmeso_mean.csv"), header = T)

df_eff <- read.csv(file.path(PATH_OUTPUT, "df_eff.csv"), head = T)
df_eff_new <- read.csv(file.path(PATH_OUTPUT, "df_eff_new_100.csv"), head = T)
df_eff_new_50 <- read.csv(file.path(PATH_OUTPUT, "df_eff_new_50.csv"), head = T)
df_eff_new_150 <- read.csv(file.path(PATH_OUTPUT, "df_eff_new_150.csv"), head = T)

# For the Sensitivity analysis (T = 10)

NLOG_VE_zero_Moz_10 <- NLOG_VE_zero_Moz[NLOG_VE_zero_Moz$NumOBS>=10,]
NLOG_VE_zero_North_10 <- NLOG_VE_zero_North[NLOG_VE_zero_North$NumOBS>=10,]
NLOG_VE_sup_zero_Moz_10 <- NLOG_VE_sup_zero_Moz[NLOG_VE_sup_zero_Moz$NumOBS>=10,]
NLOG_VE_sup_zero_North_10 <- NLOG_VE_sup_zero_North[NLOG_VE_sup_zero_North$NumOBS>=10,]
```

# I : Correlations between environmental variables (Kendall tests)

Related to Figure A1 (values not directly displayed in the paper nor in the Appendix)

```{r correlation test between environmental variable}
cor.test(NLOG_VE$chlamean, NLOG_VE$sstmean, method = "kendall")
cor.test(NLOG_VE$chlamean, NLOG_VE$slamean, method = "kendall")
cor.test(NLOG_VE$chlamean, NLOG_VE$SSCImean, method = "kendall")
cor.test(NLOG_VE$chlamean, NLOG_VE$FSLEmean, method = "kendall")
cor.test(NLOG_VE$chlamean, NLOG_VE$MNmean, method = "kendall")
cor.test(NLOG_VE$sstmean, NLOG_VE$slamean, method = "kendall")
cor.test(NLOG_VE$sstmean, NLOG_VE$SSCImean, method = "kendall")
cor.test(NLOG_VE$sstmean, NLOG_VE$FSLEmean, method = "kendall")
cor.test(NLOG_VE$sstmean, NLOG_VE$MNmean, method = "kendall")
cor.test(NLOG_VE$slamean, NLOG_VE$SSCImean, method = "kendall")
cor.test(NLOG_VE$slamean, NLOG_VE$FSLEmean, method = "kendall")
cor.test(NLOG_VE$slamean, NLOG_VE$MNmean, method = "kendall")
cor.test(NLOG_VE$SSCImean, NLOG_VE$MNmean, method = "kendall")
cor.test(NLOG_VE$FSLEmean, NLOG_VE$SSCImean, method = "kendall")
cor.test(NLOG_VE$FSLEmean, NLOG_VE$MNmean, method = "kendall")
```

# II : Differences between the environmental variables according to NLOG = 0 or NLOG > 0 (Wilcoxon tests)

Related to Figure 3

```{r comparison of means test between presence and absence}
wilcox.test(NLOG_VE_zero_Moz$chlamean,NLOG_VE_sup_zero_Moz$chlamean)
wilcox.test(NLOG_VE_zero_North$chlamean,NLOG_VE_sup_zero_North$chlamean)

wilcox.test(NLOG_VE_zero_Moz$slamean,NLOG_VE_sup_zero_Moz$slamean)
wilcox.test(NLOG_VE_zero_North$slamean,NLOG_VE_sup_zero_North$slamean)

wilcox.test(NLOG_VE_zero_Moz$SSCImean,NLOG_VE_sup_zero_Moz$SSCImean)
wilcox.test(NLOG_VE_zero_North$SSCImean,NLOG_VE_sup_zero_North$SSCImean)

wilcox.test(NLOG_VE_zero_Moz$FSLEmean,NLOG_VE_sup_zero_Moz$FSLEmean)
wilcox.test(NLOG_VE_zero_North$FSLEmean,NLOG_VE_sup_zero_North$FSLEmean)

wilcox.test(NLOG_VE_zero_Moz$MNmean,NLOG_VE_sup_zero_Moz$MNmean)
wilcox.test(NLOG_VE_zero_North$MNmean,NLOG_VE_sup_zero_North$MNmean)
```

Related to Table A1 (Sensitivity Analysis)

```{r comparison of means test with Oi,d > 10}
wilcox.test(NLOG_VE_zero_Moz_10$chlamean,NLOG_VE_sup_zero_Moz_10$chlamean)
wilcox.test(NLOG_VE_zero_North_10$chlamean,NLOG_VE_sup_zero_North_10$chlamean)

wilcox.test(NLOG_VE_zero_Moz_10$slamean,NLOG_VE_sup_zero_Moz_10$slamean)
wilcox.test(NLOG_VE_zero_North_10$slamean,NLOG_VE_sup_zero_North_10$slamean)

wilcox.test(NLOG_VE_zero_Moz_10$SSCImean,NLOG_VE_sup_zero_Moz_10$SSCImean)
wilcox.test(NLOG_VE_zero_North_10$SSCImean,NLOG_VE_sup_zero_North_10$SSCImean)

wilcox.test(NLOG_VE_zero_Moz_10$FSLEmean,NLOG_VE_sup_zero_Moz_10$FSLEmean)
wilcox.test(NLOG_VE_zero_North_10$FSLEmean,NLOG_VE_sup_zero_North_10$FSLEmean)

wilcox.test(NLOG_VE_zero_Moz_10$MNmean,NLOG_VE_sup_zero_Moz_10$MNmean)
wilcox.test(NLOG_VE_zero_North_10$MNmean,NLOG_VE_sup_zero_North_10$MNmean)
```


# III : Correlations between NLOG and environmental variables (Kendall tests)

Related to Figure 4 and Table A2

```{r correlation test between NLOG abundance and environmental variables}
cor.test(NLOG_VE_sup_zero_Moz$NLOG_stand, NLOG_VE_sup_zero_Moz$chlamean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North$NLOG_stand, NLOG_VE_sup_zero_North$chlamean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz$NLOG_stand, NLOG_VE_sup_zero_Moz$slamean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North$NLOG_stand, NLOG_VE_sup_zero_North$slamean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz$NLOG_stand, NLOG_VE_sup_zero_Moz$SSCImean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North$NLOG_stand, NLOG_VE_sup_zero_North$SSCImean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz$NLOG_stand, NLOG_VE_sup_zero_Moz$FSLEmean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North$NLOG_stand, NLOG_VE_sup_zero_North$FSLEmean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz$NLOG_stand, NLOG_VE_sup_zero_Moz$MNmean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North$NLOG_stand, NLOG_VE_sup_zero_North$MNmean, method = "kendall")

wilcox.test(NLOG_VE_sup_zero_Moz$NLOG_stand, NLOG_VE_sup_zero_North$NLOG_stand)
```

Related to Table A3 (Sensitivity Analysis)

```{r correlation test between NLOG abundance and environmental variables with Oi,d positive}
cor.test(NLOG_VE_sup_zero_Moz_10$NLOG_stand, NLOG_VE_sup_zero_Moz_10$chlamean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North_10$NLOG_stand, NLOG_VE_sup_zero_North_10$chlamean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz_10$NLOG_stand, NLOG_VE_sup_zero_Moz_10$slamean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North_10$NLOG_stand, NLOG_VE_sup_zero_North_10$slamean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz_10$NLOG_stand, NLOG_VE_sup_zero_Moz_10$SSCImean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North_10$NLOG_stand, NLOG_VE_sup_zero_North_10$SSCImean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz_10$NLOG_stand, NLOG_VE_sup_zero_Moz_10$FSLEmean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North_10$NLOG_stand, NLOG_VE_sup_zero_North_10$FSLEmean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz_10$NLOG_stand, NLOG_VE_sup_zero_Moz_10$MNmean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North_10$NLOG_stand, NLOG_VE_sup_zero_North_10$MNmean, method = "kendall")
```

# IV : Construction of models

Related to Figure 5, Table 3 and Figure A2

```{r linear models}
NLOG_VE_sup_zero_North$chlacr <- scale(NLOG_VE_sup_zero_North$chlamean)
NLOG_VE_sup_zero_North$slacr <- scale(NLOG_VE_sup_zero_North$slamean)
NLOG_VE_sup_zero_North$SSCIcr <- scale(NLOG_VE_sup_zero_North$SSCImean)
NLOG_VE_sup_zero_North$FSLEcr <- scale(NLOG_VE_sup_zero_North$FSLEmean)
NLOG_VE_sup_zero_North$MNcr <- scale(NLOG_VE_sup_zero_North$MNmean)
NLOG_VE_sup_zero_North$logNLOG <- log(NLOG_VE_sup_zero_North$NLOG_stand)

NLOG_VE_sup_zero_Moz$chlacr <- scale(NLOG_VE_sup_zero_Moz$chlamean)
NLOG_VE_sup_zero_Moz$slacr <- scale(NLOG_VE_sup_zero_Moz$slamean)
NLOG_VE_sup_zero_Moz$SSCIcr <- scale(NLOG_VE_sup_zero_Moz$SSCImean)
NLOG_VE_sup_zero_Moz$FSLEcr <- scale(NLOG_VE_sup_zero_Moz$FSLEmean)
NLOG_VE_sup_zero_Moz$MNcr <- scale(NLOG_VE_sup_zero_Moz$MNmean)
NLOG_VE_sup_zero_Moz$logNLOG <- log(NLOG_VE_sup_zero_Moz$NLOG_stand)
```

## GAM for the WIO zone

```{r LM North}
GAM_North <- mgcv::gam(logNLOG ~ s(chlacr, k = 3) + s(slacr, k = 3) + s(SSCIcr, k = 3) + s(FSLEcr, k = 3) + s(MNcr, k = 3), data = NLOG_VE_sup_zero_North)
summary(GAM_North)

GAM_North2 <- stepAIC.gam(GAM_North)
summary(GAM_North2)

par(mfrow = c(2,2))
gam.check(GAM_North2)

plot(GAM_North2,residuals=T,pages=1)
```

## Linear model for the MOZ zone

```{r LM Moz}
LM_Moz <- lm(logNLOG ~ chlacr + slacr + SSCIcr + FSLEcr + MNcr, data = NLOG_VE_sup_zero_Moz)
LM_Moz2 <- stepAIC(LM_Moz)
summary(LM_Moz2)
```

## Sensitivity analysis

Related to Table A4

```{r LM North with T equal 10}
NLOG_VE_sup_zero_North_10$chlacr <- scale(NLOG_VE_sup_zero_North_10$chlamean)
NLOG_VE_sup_zero_North_10$slacr <- scale(NLOG_VE_sup_zero_North_10$slamean)
NLOG_VE_sup_zero_North_10$SSCIcr <- scale(NLOG_VE_sup_zero_North_10$SSCImean)
NLOG_VE_sup_zero_North_10$FSLEcr <- scale(NLOG_VE_sup_zero_North_10$FSLEmean)
NLOG_VE_sup_zero_North_10$MNcr <- scale(NLOG_VE_sup_zero_North_10$MNmean)
NLOG_VE_sup_zero_North_10$logNLOG <- log(NLOG_VE_sup_zero_North_10$NLOG_stand)

GAM_North_10 <- mgcv::gam(logNLOG ~ s(chlacr) + s(slacr) + s(SSCIcr) + s(FSLEcr) + s(MNcr),
                          data = NLOG_VE_sup_zero_North_10)
GAM_North2_10 <- stepAIC.gam(GAM_North_10)
summary(GAM_North2_10)
```

```{r LM Moz with T equal 10}
NLOG_VE_sup_zero_Moz_10$chlacr <- scale(NLOG_VE_sup_zero_Moz_10$chlamean)
NLOG_VE_sup_zero_Moz_10$slacr <- scale(NLOG_VE_sup_zero_Moz_10$slamean)
NLOG_VE_sup_zero_Moz_10$SSCIcr <- scale(NLOG_VE_sup_zero_Moz_10$SSCImean)
NLOG_VE_sup_zero_Moz_10$FSLEcr <- scale(NLOG_VE_sup_zero_Moz_10$FSLEmean)
NLOG_VE_sup_zero_Moz_10$MNcr <- scale(NLOG_VE_sup_zero_Moz_10$MNmean)
NLOG_VE_sup_zero_Moz_10$logNLOG <- log(NLOG_VE_sup_zero_Moz_10$NLOG_stand)

LM_Moz_10 <- lm(logNLOG ~ chlacr + slacr + SSCIcr + FSLEcr + MNcr, data = NLOG_VE_sup_zero_Moz_10)
LM_Moz2_10 <- stepAIC(LM_Moz_10)
summary(LM_Moz2_10)
```

# V : Sampling bias analysis (Wilcoxon tests)

Related to Figure B1 and Table B1

```{r}
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$chlamean, 
            df_eff_new[df_eff_new$Zone=="MOZ",]$chlamean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$chlamean, 
            df_eff_new[df_eff_new$Zone=="WIO",]$chlamean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$slamean, 
            df_eff_new[df_eff_new$Zone=="MOZ",]$slamean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$slamean, 
            df_eff_new[df_eff_new$Zone=="WIO",]$slamean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$SSCImean, 
            df_eff_new[df_eff_new$Zone=="MOZ",]$SSCImean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$SSCImean, 
            df_eff_new[df_eff_new$Zone=="WIO",]$SSCImean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$FSLEmean, 
            df_eff_new[df_eff_new$Zone=="MOZ",]$FSLEmean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$FSLEmean, 
            df_eff_new[df_eff_new$Zone=="WIO",]$FSLEmean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$micronec_epi, 
            df_eff_new[df_eff_new$Zone=="MOZ",]$micronec_epi)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$micronec_epi, 
            df_eff_new[df_eff_new$Zone=="WIO",]$micronec_epi)
```


```{r}
#### Medians ####

## CHLA
median(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$chlamean)
median(df_eff_new[df_eff_new$Zone=="MOZ",]$chlamean)

median(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$chlamean, na.rm = T)
median(df_eff_new[df_eff_new$Zone=="WIO",]$chlamean, na.rm = T)

##SLA
median(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$slamean, na.rm = T)
median(df_eff_new[df_eff_new$Zone=="MOZ",]$slamean, na.rm = T)

median(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$slamean, na.rm = T)
median(df_eff_new[df_eff_new$Zone=="WIO",]$slamean, na.rm = T)

## SSCI
median(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$SSCImean, na.rm = T)
median(df_eff_new[df_eff_new$Zone=="MOZ",]$SSCImean, na.rm = T)

median(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$SSCImean, na.rm = T)
median(df_eff_new[df_eff_new$Zone=="WIO",]$SSCImean, na.rm = T)

## FSLE
median(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$FSLEmean, na.rm = T)
median(df_eff_new[df_eff_new$Zone=="MOZ",]$FSLEmean, na.rm = T)

median(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$FSLEmean, na.rm = T)
median(df_eff_new[df_eff_new$Zone=="WIO",]$FSLEmean, na.rm = T)

## MN
median(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$micronec_epi, na.rm = T)
median(df_eff_new[df_eff_new$Zone=="MOZ",]$micronec_epi, na.rm = T)

median(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$micronec_epi, na.rm = T)
median(df_eff_new[df_eff_new$Zone=="WIO",]$micronec_epi, na.rm = T)

```

Related to Table B2 (Sensitivity analysis of the sampled size)

```{r}
# Sampled size = 50 

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$chlamean, 
            df_eff_new_50[df_eff_new_50$Zone=="MOZ",]$chlamean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$chlamean, 
            df_eff_new_50[df_eff_new_50$Zone=="WIO",]$chlamean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$slamean, 
            df_eff_new_50[df_eff_new_50$Zone=="MOZ",]$slamean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$slamean, 
            df_eff_new_50[df_eff_new_50$Zone=="WIO",]$slamean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$SSCImean, 
            df_eff_new_50[df_eff_new_50$Zone=="MOZ",]$SSCImean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$SSCImean, 
            df_eff_new_50[df_eff_new_50$Zone=="WIO",]$SSCImean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$FSLEmean, 
            df_eff_new_50[df_eff_new_50$Zone=="MOZ",]$FSLEmean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$FSLEmean, 
            df_eff_new_50[df_eff_new_50$Zone=="WIO",]$FSLEmean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$micronec_epi, 
            df_eff_new_50[df_eff_new_50$Zone=="MOZ",]$micronec_epi)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$micronec_epi, 
            df_eff_new_50[df_eff_new_50$Zone=="WIO",]$micronec_epi)
```


```{r}
# Sampled size = 150

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$chlamean, 
            df_eff_new_150[df_eff_new_150$Zone=="MOZ",]$chlamean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$chlamean, 
            df_eff_new_150[df_eff_new_150$Zone=="WIO",]$chlamean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$slamean, 
            df_eff_new_150[df_eff_new_150$Zone=="MOZ",]$slamean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$slamean, 
            df_eff_new_150[df_eff_new_150$Zone=="WIO",]$slamean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$SSCImean, 
            df_eff_new_150[df_eff_new_150$Zone=="MOZ",]$SSCImean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$SSCImean, 
            df_eff_new_150[df_eff_new_150$Zone=="WIO",]$SSCImean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$FSLEmean, 
            df_eff_new_150[df_eff_new_150$Zone=="MOZ",]$FSLEmean)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$FSLEmean, 
            df_eff_new_150[df_eff_new_150$Zone=="WIO",]$FSLEmean)

wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="MOZ",]$micronec_epi, 
            df_eff_new_150[df_eff_new_150$Zone=="MOZ",]$micronec_epi)
wilcox.test(df_eff[df_eff$threshold=="Fisheries" & df_eff$Zone=="WIO",]$micronec_epi, 
            df_eff_new_150[df_eff_new_150$Zone=="WIO",]$micronec_epi)
```






