---
title: "Statistical analyses - simulation outputs"
author: "J. Guibert & A. Dupaix"
date: "20/11/2022 - update 23/05/2024 - 17/12/2024"
output: pdf_document
toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F) 
library(MASS)
library(mgcv)
library(dplyr)
```

\newpage

# Required data sets

```{r data frame}
WD <- ".."
PATH_OUTPUT <- file.path(WD, "Outputs_sim_smallarea")
PATH_FUNC <- file.path(WD, "Functions")
source(file.path(PATH_FUNC, "stepAIC_gam.R"))

NLOG_VE <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE.csv"), head = T)

NLOG_VE$logNLOG <- log(NLOG_VE$nlogmean)
NLOG_VE$chlacr <- scale(NLOG_VE$chlamean)
NLOG_VE$slacr <- scale(NLOG_VE$slamean)
NLOG_VE$SSCIcr <- scale(NLOG_VE$SSCImean)
NLOG_VE$FSLEcr <- scale(NLOG_VE$FSLEmean)
NLOG_VE$MNcr <- scale(NLOG_VE$MNmean)

NLOG_VE_sup_zero_Moz <- NLOG_VE %>% dplyr::filter(Zone == 'MOZ', nlogmean > 0)
NLOG_VE_sup_zero_North <- NLOG_VE %>% dplyr::filter(Zone == 'WIO', nlogmean > 0)

# NLOG_VE_zero <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_zero.csv"), head = T)
# 
# NLOG_VE_zero_Moz <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_zero_Moz.csv"), head = T)
# NLOG_VE_zero_North <- read.csv(file.path(PATH_OUTPUT, "NLOG_VE_zero_North.csv"), head = T)
# 
# dfMN_epi<-read.csv(file.path(PATH_OUTPUT, "MN_epi_mean.csv"), header = T)
# dfMN_u<-read.csv(file.path(PATH_OUTPUT, "MN_umeso_mean.csv"), header = T)
# dfMN_mu<-read.csv(file.path(PATH_OUTPUT, "MN_mumeso_mean.csv"), header = T)
# dfMN_ml<-read.csv(file.path(PATH_OUTPUT, "MN_mlmeso_mean.csv"), header = T)
# dfMN_hml<-read.csv(file.path(PATH_OUTPUT, "MN_hmlmeso_mean.csv"), header = T)

# df_eff <- read.csv(file.path(PATH_OUTPUT, "df_eff.csv"), head = T)
# df_eff_new <- read.csv(file.path(PATH_OUTPUT, "df_eff_new_100.csv"), head = T)
# df_eff_new_50 <- read.csv(file.path(PATH_OUTPUT, "df_eff_new_50.csv"), head = T)
# df_eff_new_150 <- read.csv(file.path(PATH_OUTPUT, "df_eff_new_150.csv"), head = T)

# For the Sensitivity analysis (T = 10)

# NLOG_VE_zero_Moz_10 <- NLOG_VE_zero_Moz[NLOG_VE_zero_Moz$NumOBS>=10,]
# NLOG_VE_zero_North_10 <- NLOG_VE_zero_North[NLOG_VE_zero_North$NumOBS>=10,]
# NLOG_VE_sup_zero_Moz_10 <- NLOG_VE_sup_zero_Moz[NLOG_VE_sup_zero_Moz$NumOBS>=10,]
# NLOG_VE_sup_zero_North_10 <- NLOG_VE_sup_zero_North[NLOG_VE_sup_zero_North$NumOBS>=10,]
```

# I : Correlations between environmental variables (Kendall tests)

Related to Figure A1 (values not directly displayed in the paper nor in the Appendix)

```{r correlation test between environmental variable}
# cor.test(NLOG_VE$chlamean, NLOG_VE$sstmean, method = "kendall")
# cor.test(NLOG_VE$chlamean, NLOG_VE$slamean, method = "kendall")
# cor.test(NLOG_VE$chlamean, NLOG_VE$SSCImean, method = "kendall")
# cor.test(NLOG_VE$chlamean, NLOG_VE$FSLEmean, method = "kendall")
# cor.test(NLOG_VE$chlamean, NLOG_VE$MNmean, method = "kendall")
# cor.test(NLOG_VE$sstmean, NLOG_VE$slamean, method = "kendall")
# cor.test(NLOG_VE$sstmean, NLOG_VE$SSCImean, method = "kendall")
# cor.test(NLOG_VE$sstmean, NLOG_VE$FSLEmean, method = "kendall")
# cor.test(NLOG_VE$sstmean, NLOG_VE$MNmean, method = "kendall")
# cor.test(NLOG_VE$slamean, NLOG_VE$SSCImean, method = "kendall")
# cor.test(NLOG_VE$slamean, NLOG_VE$FSLEmean, method = "kendall")
# cor.test(NLOG_VE$slamean, NLOG_VE$MNmean, method = "kendall")
# cor.test(NLOG_VE$SSCImean, NLOG_VE$MNmean, method = "kendall")
# cor.test(NLOG_VE$FSLEmean, NLOG_VE$SSCImean, method = "kendall")
# cor.test(NLOG_VE$FSLEmean, NLOG_VE$MNmean, method = "kendall")
```

# III : Correlations between NLOG and environmental variables (Kendall tests)

Related to Figure 4 and Table A2

```{r correlation test between NLOG abundance and environmental variables}
cor.test(NLOG_VE_sup_zero_Moz$nlogmean, NLOG_VE_sup_zero_Moz$chlamean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North$nlogmean, NLOG_VE_sup_zero_North$chlamean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz$nlogmean, NLOG_VE_sup_zero_Moz$slamean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North$nlogmean, NLOG_VE_sup_zero_North$slamean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz$nlogmean, NLOG_VE_sup_zero_Moz$SSCImean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North$nlogmean, NLOG_VE_sup_zero_North$SSCImean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz$nlogmean, NLOG_VE_sup_zero_Moz$FSLEmean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North$nlogmean, NLOG_VE_sup_zero_North$FSLEmean, method = "kendall")

cor.test(NLOG_VE_sup_zero_Moz$nlogmean, NLOG_VE_sup_zero_Moz$MNmean, method = "kendall")
cor.test(NLOG_VE_sup_zero_North$nlogmean, NLOG_VE_sup_zero_North$MNmean, method = "kendall")

wilcox.test(NLOG_VE_sup_zero_Moz$nlogmean, NLOG_VE_sup_zero_North$nlogmean)
```

# IV : Construction of models
## GAM for the WIO zone

```{r}
GAM_North <- mgcv::gam(logNLOG ~ s(chlacr, k = 6) + s(slacr, k = 6) +
                         s(SSCIcr, k = 6) + s(FSLEcr, k = 6) + s(MNcr, k = 6),
                       data = NLOG_VE_sup_zero_North)
summary(GAM_North)

GAM_North2 <- stepAIC.gam(GAM_North)
summary(GAM_North2)

par(mfrow = c(2,2))
gam.check(GAM_North2)

plot(GAM_North2,residuals=T,pages=1)
```

## Linear model for the MOZ zone

```{r LM Moz}
LM_Moz <- lm(logNLOG ~ chlacr + slacr + SSCIcr + FSLEcr + MNcr, data = NLOG_VE_sup_zero_Moz)
LM_Moz2 <- stepAIC(LM_Moz)
summary(LM_Moz2)

par(mfrow = c(2, 2))
plot(LM_Moz2)
```

## GAM for the MOZ zone

```{r GAM Moz}
GAM_Moz <- mgcv::gam(logNLOG ~ s(chlacr, k = 6) + s(slacr, k = 6) +
                       s(SSCIcr, k = 6) + s(FSLEcr, k = 6) + s(MNcr, k = 6),
                     data = NLOG_VE_sup_zero_Moz)
summary(GAM_Moz)

GAM_Moz2 <- stepAIC.gam(GAM_Moz)
summary(GAM_Moz2)

par(mfrow = c(2,2))
gam.check(GAM_Moz2)

plot(GAM_Moz2,residuals=T,pages=1)
```

